Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-09-19 src/docs_12-05-22-mrc-gida/12-05-22-mrc-gida.Rmd
mrc-gida upload

df_area_age_behav <- df %>%
  select(area_id, age_group, population_nosex12m, incidence_nosex12m, starts_with("population_sex"), starts_with("incidence_sex")) %>%
  pivot_longer(
    cols = starts_with("population") | starts_with("incidence"),
    names_to = c("indicator", "category"),
    names_sep = "_"
  ) %>%
  pivot_wider(
    id_cols = c("area_id", "age_group", "indicator", "category"),
    names_from = "indicator",
    values_from = "value"
  )
```

@@

```{r echo=FALSE, out.width = "350px", fig.cap = "New infections reached prioritising according to different stratifications."}
knitr::include_graphics("depends/infections-reached.png")
```

```{r echo=FALSE, out.width = "350px", fig.cap = "As previous slide but specific to Mozambique."}
knitr::include_graphics("depends/infections-reached-moz.png")
```

>>>>

df_area_age_behav <- df %>%
  select(area_id, age_group, population_nosex12m, incidence_nosex12m, starts_with("population_sex"), starts_with("incidence_sex")) %>%
  pivot_longer(
    cols = starts_with("population") | starts_with("incidence"),
    names_to = c("indicator", "category"),
    names_sep = "_"
  ) %>%
  pivot_wider(
    id_cols = c("area_id", "age_group", "category"),
    names_from = "indicator",
    values_from = "value"
  )
```

@@

```{r echo=FALSE, out.width = "350px", fig.cap = "New infections reached prioritising according to different stratifications."}
knitr::include_graphics("depends/infections-reached.pdf")
```
